---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file. -->
<!-- The code to render this README is stored in .github/workflows/render-readme.yaml -->
<!-- Variables marked with double curly braces will be transformed beforehand: -->
<!-- `packagename`, `department`, `department_url`, `institution`, `recon`, `recon_description` is extracted from the DESCRIPTION file -->
<!-- `gh_repo` is extracted via a special environment variable in GitHub Actions -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {{ packagename }} <img src="man/figures/logo.svg" align="right" width="120" />

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/license/mit/)
[![R-CMD-check](https://github.com/{{ gh_repo }}/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/{{ gh_repo }}/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/{{ gh_repo }}/branch/main/graph/badge.svg)](https://app.codecov.io/gh/{{ gh_repo }}?branch=main)
[![lifecycle-{{ recon }}](https://www.reconverse.org/images/badge-{{ recon }}.svg)](https://www.reconverse.org/lifecycle.html#{{ recon }})
<!-- badges: end -->

{{ packagename }} provides functions to ....

<!-- This sentence is optional and can be removed -->
{{ packagename }} is developed at the [{{ department }}]({{ department_url }}) at the {{ institution }} as part of the [Epiverse-TRACE program](https://data.org/initiatives/epiverse/).

## Installation

You can install the development version of {{ packagename }} from
[GitHub](https://github.com/) with:

```{r eval=TRUE}
# install.packages("pak")
pak::pak("{{ gh_repo }}")
library("{{ packagename }}")
```

## Example

These examples illustrate some of the current functionalities


## Development

## Related packages and Limitations


### Lifecycle

This package is currently *{{ recon }}*, as defined by the [RECON software
lifecycle](https://www.reconverse.org/lifecycle.html).


### Contributions

Contributions are welcome via [pull requests](https://github.com/{{ gh_repo }}/pulls).

### Code of Conduct

Please note that the {{ packagename }} project is released with a 
[Contributor Code of Conduct](https://github.com/epiverse-trace/.github/blob/main/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.